\LaTeXe\ guide for the Journal of Functional Programming

### 2019-10-21 papers/jfp/7-experience.tex
Update reference

These powerful and modular abstractions, which ultimately formed part
of the conceptual structure of the paper, emerged fairly late in the
project as we repeatedly reviewed, redesigned, and refactored our
executable prototypes. It is hard to believe that we could have
developed them without the support of Haskell as a design language.

>>>>

\noindent
These powerful and modular abstractions, which ultimately formed part
of the conceptual structure of the paper, emerged fairly late in the
project as we repeatedly reviewed, redesigned, and refactored our
executable prototypes. It is hard to believe that we could have
developed them without the support of Haskell as a design language.
